% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 10pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---
\usepackage{comment}
% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{\href{https://www.linkedin.com/in/kaustubh-venkatesh-475903210/}{Kaustubh Venkatesh}}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: kaustubhv@hotmail.com      &
\hspace{0.55in} \textbf{GitHub}: \href{https://github.com/kaustubhv5500}{kaustubhv5500}    &
\hspace{0.4in}  \textbf{Address}: E-803, Anmol CHS,  \\

% Line 2: Phone number, LinkedIn, citizenship
\hspace{0.45in} kaustubh.v@spit.ac.in      &
\hspace{0.55in} \textbf{Phone}: +91-8425909786   & 
\hspace{0.4in} Goregaon West, Mumbai-104
% \hspace{1.03in} Goregaon West, Mumbai
\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

\nohyphens{\color{OliveGreen}{Research interests}}
& Digital Communication \& Signal Processing, RF System Design, Machine Learning \& Data Analytics, Neural networks \\
& \\

% --- Section: Education ---

\color{OliveGreen}{Education} 
& \textbf{Sardar Patel Institute of Technology} \hfill Mumbai, India \\ 
& Bachelors in Electronics and Telecommunication Engineering \\
& July 2018 -- Present \\
& {\it GPA: 9.72/10}\\
& \\

& \textbf{R.N. Podar School} \hfill Mumbai, India \\
& Grade 12\\
& April 2016 -- May 2018\\
& {\it Percentage: 97.6\%}\\
& \\

& \textbf{SSPM's Sri Sri Ravishankar Vidya Mandir} \hfill Mumbai, India\\
& Grade 10 \\
& 2010 -- March 2016 \\
& {\it Cumulative GPA: 10}\\
& \\

% --- Uncomment the next few lines if you want to include some courses ---
\color{OliveGreen}{Coursework}
& \underline{Electronics} : Analog \& Digital Electronics, Microprocessors 
\& Microcontrollers, Embedded Systems, Control Systems, Integrated Circuits, HDL Programming, PCB Design \& Soldering \\

& \underline{Communications} : Analog \& Digital Communications, Digital Signal Processing, RF Antenna Design, Computer Networks, Random Signal Analysis \\

& \underline{Electives} : Advanced Data Structures \& Algorithms, Statistics \& Data Analytics, Machine Learning, Law for Engineers, German Language\\
 \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---

{\color{OliveGreen}{Awards and}} 
& \href{https://coursera.org/share/873ac303647846970ff59ac138eee553}{IT Fundamentals for Cyber Security by IBM}\\
{\color{OliveGreen}{Certifications}} 
& Microsoft Azure Fundamentals certification course by Ernst \& Young.\\
& College to Corporate Training by JP Morgan \& Chase India Ltd. \\
& Green Revolution Global Certification by the UNFCCC.\\
% UN Framework Convention on Climate Change. \\
& Awarded the ‘Academic Excellence Award’ for the year 2015-2016. \\
& \\

% --- Section: Publications ---
\nohyphens{\color{OliveGreen}{Projects \& Publications}} 
& \textbf{Identification of Multiple Copy-move Attacks in Digital Images using FFT and CNN} \\
& Gokul Nair, Kaustubh Venkatesh, Dipankar Sen, Reena Sonkusare \\
& \textit{2021 12th International Conference on Computing, Communication and Networking Technologies (ICCCNT).} DOI : add doi \\
& \\

& \textbf{Implementation of a Machine Learning based OFDM detector using GNU Radio} \\
& Kaustubh Venkatesh, Gokul Nair, Sukanya Kulkarni. \\
& \textit{2021 International Conference on Communication Information and Computing Technology (ICCICT).} DOI : \href{https://ieeexplore.ieee.org/document/9510060}{10.1109/ICCICT50803.2021.9510060} \\
& \\

& \textbf{Pneumonia Detection from Chest X-ray using Transfer Learning} \\
& Sharvari Kalgutkar, Vansh Jain, Gokul Nair, Kaustubh Venkatesh, Kshitij Parab. \\
& \textit{2021 IEEE 6th International Conference for Convergence in Technology (I2CT).}\\
& DOI : \href{https://ieeexplore.ieee.org/document/9417872}{10.1109/I2CT51068.2021.9417872}\\
\\


% --- Section: Industry experience ---

{\color{OliveGreen}{Industry experience}}
& {\textbf{Analystt.ai Technology Pvt. Ltd.}} \hfill Mumbai, India\\
& Software Development Intern \hfill May 2021 – August 2021 \\
& Woked with a team of ten to develop an AI driven dashboard with financial information and lead generation using Django, React and FastAPI.\\
& \\

& {\textbf{Location Guru Services Pvt. Ltd.}} \hfill Mumbai, India\\
& Machine Learning \& Data Science Intern \hfill June 2019 – July 2019 \\
& Developed an application / API to analyze location data and predict trends for phone carriers using Machine Learning in Python. \\
& \\
 
& {\textbf{Real World Promotions Pvt. Ltd.}} \hfill Mumbai, India\\
& Software Development Intern \hfill October 2018 – January 2019 \\
& Created Reporting Formats and Web Interfaces as well as helping in communicating with the field force for effective management of  resources.\\
& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

{\color{OliveGreen}{Skills}} 
& \textbf{Programming}\\
& Proficient in: Python, MATLAB, C. \\
& Familiar with: Java, C++, R, ARM Assembly, MySQL, \LaTeX. \\
& Platforms : VS Code, Anaconda, Arduino, Keil $\mu$Vision, ROS, Django, Proteus, Linux, Git, Docker, React \\
& \\

& \textbf{Languages} \\
& Proficient: English, Hindi, Tamil\\
& Familiar: German \\
& \\

% --- Section: Service and outreach ---

\color{OliveGreen}{Service and outreach}
& \textbf{Abhyudaya, An NGO founded by SPJIMR} \hfill July 2019 – March 2020 \\
& Taught Mathematics and Science to underprivileged students from nearby schools. \\
& \\

% --- Section: Professional society memberships ---
% --- Note: section title is spread over two lines ---

{\color{OliveGreen}{Professional}} 
& {\textbf{SPark, SPIT’s Official Editorial}} \hfill \\
{\color{OliveGreen}{Memberships}} 
& Managing Editor, Columns \hfill August 2020 – Present \\
& Senior Correspondent, Reporting \hfill August 2019 – May 2020\\
& Junior Correspondent, Reporting \hfill August 2018 – May 2019 \\
& \\
& Wrote and edited various articles for the Editorial’s Website. Part of the organizing committee for SPIT’s Open Mic 2020 \& 2021. Part of the organizing committee for SPIT’s Model United Nations Conference, 2019. Official contributor for SPIT’s Annual Newsletter for 2019 and 2020.\\
\\

& {\textbf{IEEE Student Member}} \hfill May 2021 - December 2021\\
& Bombay Section\\
& \\
\\

% --- Section: References ---
\nohyphens{\color{OliveGreen}{References}} 
& \textbf{Dr. Sukanya Kulkarni} \\
& Associate Professor,\\
& Department of Electronics and Telecommunication Engineering \\
& Sardar Patel Institute of Technology. \\
& Courses Taught : Analog/Digital Communications\\
& \textit{Email : sukanya\_kulkarni@spit.ac.in }\\
& \\

& \textbf{Dr. Reena Sonkusare} \\
& Head of Department,\\
& Department of Electronics and Telecommunication Engineering \\
& Sardar Patel Institute of Technology. \\
& Courses Taught : RF Antenna Design, Digital Signal Processing \\
& \textit{Email : reena\_kumbhare@spit.ac.in}\\
& \\

& \textbf{Dr. Amol Deshpande} \\
& Assistant Professor,\\
& Department of Electronics and Telecommunication Engineering \\
& Sardar Patel Institute of Technology. \\
& Courses Taught : Electromagnetic Waves, Signals \& Systems, Random Signal Analysis \\
& \textit{Email : amol\_deshpande@spit.ac.in}\\
& \\


% --- Section: Other interests/hobbies ---

\nohyphens{\color{OliveGreen}{Other interests}} & Online Gaming, Formula 1, Cricket\\

% --- End of CV! ---

\end{longtable}
\end{document}
