---
title: "STC LAB 3 : Regression Analysis"
author:
  - name : "Kaustubh Venkatesh"
  - name : "UID : 2018120033"
  - name : "Date : 10-08-2020"
output:
  html_notebook: default
---
```{r}
#R version info
version
```

```{r}
library(lattice)
library(DAAG)
library(ggplot2)
df = mtcars
head(mtcars)
```

```{r}
#Simple linear regression model development
ggplot(data=df, aes(x=wt, y=mpg)) +
  geom_point() +
  stat_smooth(method = "lm", col = "red")
```
```{r}
#boxplot of wt vs mpg
boxplot(mtcars$mpg, horizontal=TRUE)
title(main="box plot of mpg vs wt",xlab="mpg")
```
```{r}
d <- density(mtcars$mpg)
plot(d, main="Kernel Density of Miles Per Gallon")
polygon(d, col="red", border="blue")
```


```{r}
#building the simple linear regression model
model = lm(mpg ~ wt, data=df)
summary(model)
```

```{r}
#choosing random value of weight to predict value of mpg
test = data.frame(wt=3.65)
pred = predict(model,test)
coefficients((model))
cat("Correlation between weight and mpg is : ", cor(df$mpg,df$wt))
cat("\nPredicted value : ",pred)
```
```{r}
#multiple linear regression wrt weight, automatic and horsepower
multimodel = lm(mpg ~ wt + am + hp, data = df)
summary(multimodel)
```
```{r}
#Test date to predict the value of mpg based on multiple regression
test1 = data.frame(wt = 3.69, am = 1, hp = 100)
pred_multi = predict(multimodel, test1)
coefficients(multimodel)
cat("Predicted value : ", pred_multi)
```
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
<strong>Conclusion : </strong>
<br/>
From the experiment conducted, it can be concluded that regression is an important statistical tool which helps us determine 
relations between different attributes in a dataset which then allows us to predict values based on different features.
R contains various functions which allow us to  visualise data graphically as well as to build simple and multiple linear regression models.

</div>
