---
title: 'STC LAB 3-2 : Logistic & Multinomial  Regression'
author:
  - name : "Kaustubh Venkatesh"
  - name : "UID : 2018120033"
  - name : "Date : 24-08-2020"
output: 
    html_notebook: default
---

```{r}
#R version info
version
```
```{r}
#Reading the dataset
df = read.csv("binary.csv")
head(df)
```
```{r}
#Structure of data frame
str(df)
```

```{r}
#Data pre-processing
df$admit = as.factor(df$admit)

#Using xtabs to analyse the relationship of the data
xtabs(~admit + rank, data = df)
```
```{r}
#Splitting data into test and train data-sets making sure pattern can be reproduced
set.seed(1234)
ind = sample(2, nrow(df), replace = TRUE, prob = c(0.80,0.20))
test = df[ind==1,]
train = df[ind==2,]
head(test)
```

```{r}
#Building the regression model
#Response variable : admit
#Independent variables : gre, gpa, rank
clf = glm(admit~ gpa + rank, data = df, family = 'binomial')
summary(clf)
```
```{r}
#Coefficients of the model created
coefficients(clf)
```
```{r}
#Predicting outcomes of test data-set using the model generated
pred = predict(clf , test, type = 'response')
head(pred)
```
```{r}
#To evaluate model performance, accuracy and mis-classification using confusion matrix
pred2 = ifelse(pred > 0.5, 1, 0)
tab = table(Predicted = pred2, Actual = test$admit)
acc = sum(diag(tab))/sum(tab)
tab
cat("Accuracy : ", acc*100, "%")
```
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
<strong>Conclusion : </strong>
<br/>
From the experiment conducted, it can be concluded that logistic and multi-nomial regression is used to model the probability of a certain class or event existing such as pass/fail, win/lose etc. Each object being detected in the image would be assigned a probability between 0 and 1, with a sum of one. R has an inbuilt function glm() which allows us to generate a general linear regression model using the data provided to it,

</div>
